\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-18 main.Rmd
done with case study section

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households. Is there any untold story from these plots? Figure \ref{fig:household13} lays out the data points at the finest time resolution in a $3 \times 4$ monthly grid, for household 1 and 3. Household 1 was on vacation over three weeks of June, and household 2 was also away for holidays from September to early October and late June to mid July in the past year. This calendar plot evidently fills the missing piece of the picture. Also weekday and weekend

```{r h12, fig.height = 10, fig.cap = "Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \\ref{fig:dow} and \\ref{fig:hod}."}
```

```{r h34, fig.height = 10, fig.cap = "Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \\ref{fig:dow} and \\ref{fig:hod}."}
```

>>>>

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical toolkits, are useful for summarizing overall deviations across days and households. Figure \ref{fig:h12} and \ref{fig:h34} apply the new calendar displays individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their weekday energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h12, fig.height = 10, fig.cap = "Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h34, fig.height = 10, fig.cap = "Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating."}
```

### 2018-10-18 main.tex
done with case study section

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the weekdays given the medians, compared to the others consisting of one
or two people. Whereas, household 2 displays a great deal of variability
in daily energy consumption with noticeable variations on Thursdays, and
much higher usage over the weekends. The other two households (1 and 4)
tend to consume more energy on average with increased variations during
the weekends relative to the weekdays, as a reflection of work and
leisure routines.

@@

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical
toolkits, are useful for summarizing overall deviations across days and
households. Is there any untold story from these plots? Figure
\ref{fig:household13} lays out the data points at the finest time
resolution in a \(3 \times 4\) monthly grid, for household 1 and 3.
Household 1 was on vacation over three weeks of June, and household 2
was also away for holidays from September to early October and late June
to mid July in the past year. This calendar plot evidently fills the
missing piece of the picture. Also weekday and weekend

@@

\caption{Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \ref{fig:dow} and \ref{fig:hod}.}\label{fig:h12}
\end{figure}

@@

\caption{Arranging sub-daily energy usage into monthly grids reveals the vacation time periods for households 1 and 3, which are hidden in Figure \ref{fig:dow} and \ref{fig:hod}.}\label{fig:h34}
\end{figure}

>>>>

Figure \ref{fig:dow} shows the energy use across days of week in the
form of letter value plots \citep{hofmann2017letter}. As a variant of
boxplots, letter value plots represent each pair of adjacent letter
values using one box, instead of whiskers. Figure \ref{fig:dow}
demonstrates three letter values and outliers marked as asterisks, with
a line representing the median (thus M) and the innermost boxes
corresponding to the fourth (F) and the eighth quantiles (E). Household
3, with a family size of one couple and two kids, uses more energy over
the weekdays given the medians, compared to the others consisting of one
or two people. Whereas, household 2 displays a great deal of variability
in daily energy consumption with noticeable variations on Thursdays, and
much higher usage over the weekends. The other two households (1 and 4)
tend to consume more energy on average with increased variations during
the weekends relative to the weekdays, as a reflection of work and
leisure patterns.

@@

Figure \ref{fig:dow} and \ref{fig:hod}, part of traditional graphical
toolkits, are useful for summarizing overall deviations across days and
households. Figure \ref{fig:h12} and \ref{fig:h34} apply the new
calendar displays individually for each household, unfolding their
day-to-day life. Glancing through Figure \ref{fig:h12}, their weekday
energy use distinguishes from their weekends. We can exactly tell when
their air conditioner and heater are turned on. Heating keeps
functioning in consecutive hours at household 2, which is evident in the
mid July; while household 1 uses them cautiously. This finding helps
explain the strips and clusters in Figure \ref{fig:hod}. The calendar
plots speak the stories about vacation time that are untold by previous
figures. Household 1 is on vacation over three weeks of June, and
household 2 was also away for holidays during Christmas and the second
week of June. Figure \ref{fig:h34} shows household 3 takes two
one-month-long family trips in September till early October and in
June/July, and household 4 is away over two or three weeks in early
October, December and late June. The use of air conditioning and heating
leaves no trace in these two households.

@@

\caption{Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June.}\label{fig:h12}
\end{figure}

@@

\caption{Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating.}\label{fig:h34}
\end{figure}
